---
title: "Calculating Montly Mean Counts of Antagonistic Tweet Counts"
author: "Sefa Ozalp"
date: 2017-11-09
output: html_document
---

<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```

<!-- Add your analysis here -->

## Data Wrangling
This is a quick script to calculate mean monthly counts of antagonistic speech in the data set. 


First data I/O and converting to time series.


```{r, results='hide', warning=FALSE, message=FALSE}
options(digits=3)
library(data.table)
library(tidyverse)
extrafont::loadfonts()
library(xts)
library(hrbrthemes)

complete_dataset <- fread("~/Documents/Work/CST/event_data/big.dataset.complete.dataset.raw_GeoAgentsandHate.csv", stringsAsFactors = F)

complete_dataset$tweet.time.posix <- complete_dataset$tweet.time.posix %>% as.POSIXct()

antagonistic_subset <- complete_dataset %>% 
  select(classifier.hate.yes, tweet.time.posix) %>% 
  mutate(tweet.time.posix= as.Date(tweet.time.posix), classifier.hate.yes= as.numeric(classifier.hate.yes)) %>% 
  replace_na(., list(classifier.hate.yes=0))
  
ts_antagonistic<- xts(x = antagonistic_subset$classifier.hate.yes, order.by = antagonistic_subset$tweet.time.posix)
ts_sum_antagonistic <- apply.daily(ts_antagonistic,sum)
ts_sum_df_antagonistic <- data.frame(date=index(ts_sum_antagonistic), coredata(ts_sum_antagonistic))
colnames(ts_sum_df_antagonistic)=c('date','sum')


```

## Plot

Next, lets take a look at the antagonistic time series plot again. 


```{r, out.width=8,out.height=7}

b <- ggplot(ts_sum_df_antagonistic)+
     geom_line(aes(x=date,y=sum), colour="red")+
     labs( x= 'Time (Daily)', y= "Tweet Count",
           title = "Timeseries Plot of Tweet Counts For Tweets \nClassified as Antagonistic ", 
           #subtitle = "Graph 2", 
           caption = "Social Data Science Lab") +
     theme_ipsum_rc()+
     scale_x_date(date_breaks = "1 month",date_labels = ("%b-%y"))

b

```


## Results

Finally here is the information we have been looking for.
 
```{r}
start(ts_antagonistic) # first day of the dataset
end(ts_antagonistic) # last day of the dataset

monthly <- apply.monthly(ts_antagonistic,sum)
monthly <- data.frame(date=index(monthly),coredata(monthly))
# monthly %>% glimpse()

summary_mean <- monthly %>% 
  mutate(pre_first_peak= ifelse(date<"2016-05-01", 1, 0)) %>% #selected first day of May as the peak ends then 
  group_by(pre_first_peak) %>% 
  summarise(., mean(coredata.monthly.)) %>% 
  select(pre_first_peak=pre_first_peak, mean_antag_count=`mean(coredata.monthly.)`)

summary_mean #pre/post peak-1 smmary mean antagonistic tweet count table

pre_count <- round(summary_mean$mean_antag_count[2], 2)
post_count <- round(summary_mean$mean_antag_count[1], 2)
  
```

As seen above, mean monthly antagonistic tweet count before the first peak is **`r pre_count `**; whereas mean monthly antagonistic tweet count is 
**`r post_count `**. 

 
 
## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
